Outstanding Title

### 2017-04-17 writing/EpiDraft.Rmd
Simulate Legionnaire-like data

@@

>>>>

###Actual Data from the CDC

@@

### Simulated Data with Similar Trend

Many epidemiologic data sets are of a sensitive nature and not publicly available.  We can use eesim to simulate data with a similar seasonal trend to fit and assess models.

```{r, echo=F}
exposure <- continuous_exposure(n=1001, mu = 65, sd = 3, trend = "cos1", amp=.4)
#Make this into weekly data instead of daily.
exposuremat <- matrix(data=exposure$x, ncol = 7, nrow=143, byrow=T)
exposurex <- apply(exposuremat, 1, mean)
newdate <- seq.int(from=exposure$date[1], to=exposure$date[1001], by=7)
weeklyexp <- data.frame(date=newdate, x=exposurex)
plot(weeklyexp, main = "Plot of Exposure values")
outcome <- sim_outcome(weeklyexp, average_outcome = 10, trend = "linear")
plot(outcome$outcome)

#Try with eesim function

```
